---
title: "Homework 1"
author: "Berkay Bor 20080474"
---

```{r global_options, include=FALSE}
# Do not delete or modify this chunk.
# We will cover chunk options later.
# This is required for Question 7
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**Question 1** With Markdown write a sentence that has one word in bold.

Garry's Mod is **overrated**.

**Question 2** With Markdown write a sentence that has one word in italic.

_Human_ is a social animal.

**Question 3** With Markdown write a sentence that has one word in italic bold.

**_Katalin Novak_** is the President of Hungary

**Question 4** With Markdown write an unordered list with three items.

Shopping List:

* Egg
* Milk
* Tomato


**Question 5** With Markdown write an ordered list with three items.

My favourite sitcoms I've ever watched:

1. Line of Duty
2. The Walking Dead
3. How I Met Your Mother?

**Question 6** With Markdown give a link to your favorite webpage.

[Amazon](https://www.amazon.com.tr/)

**Question 7** With Markdown add a cat picture.

![Garfield](https://hbomax-images.warnermediacdn.com/images/GWUFN8AfNooudjgEAAABv/tile?size=1280x720&format=jpeg&partner=hbocom&v=f9a696f216baff0af72055d135505b58&host=art-gallery.api.hbo.com&w=1200)

**Question 8** With Rmarkdown insert a code chunk and give an example of a simple mathematical calculation in it.

```{r}
9*9
```


**Question 9** With $LaTeX$ write your favorite equation in block form.

$Q=m*c*\Delta*t$

**Question 10** In a code chunk calculate 3 + 4.

```{r}
3+4
```

